{Good covers and algebras on conically smooth spaces}

### 2025-08-21 paperversion/paper.tex
mini fixes

\begin{abstract}
    We construct good covers for conically smooth spaces {\color{MidnightBlue} over depth-$1$ posets}. By a result of Karlsson--Scheimbauer--Walde, this implies that, for every such space $X$, constructible factorisation algebras on $X$ and disk algebras over $X$ coincide. We also give a simplified proof of that result.
\end{abstract}

@@

\begin{lemma}\label{2978BNV}
    Every smooth manifold $M$ has a good cover $\mcal{U}$ which is generated by extendable basics.
\end{lemma}
\begin{proof}
    Equip $M$ with a riemannian metric. We can put $\mcal{U}=\langle\mcal{V}\rangle$ for $\mcal{V}=\{D_p\}_{p\in M}$ where $D_p$ is the convex disk which is the interior of the image of a ball in $\Tangent_p M$ under the exponential map, with radius strictly smaller than the radius of injectivity.
\end{proof}

>>>>

\begin{abstract}
    We construct good covers for conically smooth spaces. By a result of Karlsson--Scheimbauer--Walde, this implies that, for every such space $X$, constructible factorisation algebras on $X$ and disk algebras over $X$ coincide. We also give a simplified proof of that result.
\end{abstract}

@@

\begin{lemma}\label{2978BNV}
    Every smooth manifold $M$ has a good cover $\mcal{U}$ which is generated by extendable basics.
\end{lemma}
\begin{proof}
    Equip $M$ with a riemannian metric. We can put $\mcal{U}=\langle\mcal{V}\rangle$ for $\mcal{V}=\{D_p\}_{p\in M}$ where $D_p$ is the convex disk which is the interior of the image of a ball in $\Tangent_p M$ under the exponential map, with a radius that is strictly smaller than the radius of injectivity.
\end{proof}
